---
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Problem 1

```{r}
# Load libraries
library(dplyr) 
library(magrittr)
library(tidyr)
library(car)
```

## Load Medical Insurance Dataset

```{r}
ins_df = read.csv("insurance.csv")
head(ins_df)
```

### Linear Regression Model with discrete variables
```{r}
# Remove continuous predictors
subset_ins_df <- subset(ins_df, select = -c(age, bmi))
head(subset_ins_df)
```
### Transform categorical variables
```{r}
# Turn the categorical variables and ordinal numeric into factors
subset_ins_df$sex = as.factor(subset_ins_df$sex)
subset_ins_df$children = as.factor(subset_ins_df$children)
subset_ins_df$smoker = as.factor(subset_ins_df$smoker)
subset_ins_df$region = as.factor(subset_ins_df$region)
```

```{r}
# Fit the linear regression model predicting insurance charges
fit <- lm(data=subset_ins_df, charges ~ sex + children + smoker + region)
# Show coefficients, standard errors, and p values
summary(fit)
```

### Checking Assumptions

The residuals do not follow a random pattern and we cannot assume mean zero or linearity. The relationship between these discrete variables is not well represented by a linear model. From the summary table, the variances are not constant as well so we cannot assume homoscedasticity. Lastly, checking the qq plot does not indicate normality as the right side of the graph is longer and does not align with normality expectation. Forming a linear regression model with only discrete variables from the insurance dataset violates all of the standard assumptions. 

```{r}
# Residuals against fitted values
plot(fit, which=1, pch=16)
```

```{r}
# Check relationship between predictor variables
pairs(data=subset_ins_df, charges ~ ., pch=16, cex=1.5)
```
```{r}
# Check residuals
residualPlots(fit)
```

```{r}
# Check normality
qqPlot(residuals(fit))

```

### Problem 2
```{r}
B = 200

n <- nrow(subset_ins_df) # Get n
fit <- lm(data=subset_ins_df, charges ~ sex + children + smoker + region) # Fit a linear model

coef.boot <- matrix(0, B, 11) # store slope and intercept
for (b in 1:B) {
  indices = sample(seq(1,n), size=n, replace=T) # Get random indices
  boot_sample = subset_ins_df[indices, ] 

  m.boot = lm(data=boot_sample, charges ~ sex + children + smoker + region) # refit the model
  
  colnames(coef.boot) = c("intercept_se_boot", "sexmale_se_boot", "children1_se_boot", "children2_se_boot", "children3_se_boot", "children4_se_boot", "children5_se_boot", "smokeryes_se_boot", "regionnorthwest_se_boot", "regionsoutheast_se_boot", "regionsouthwest_se_boot")
  
  coef.boot[b,1:11] = summary(m.boot)$coefficients[,2] # Get bootstrap coefficients
  
}
  
head(coef.boot)
```




